maze-dataset: Maze Generation with Algorithmic Variety and Representational Flexibility

### 2025-05-28 docs/paper/paper.tex
wip

Autoregressive transformer models can be quite sensitive to the exact
format of input data, and may even use delimiter tokens to perform
reasoning steps (\protect\hyperlink{ref-pfau2024dotbydot}{Pfau et al.,
2024}; \protect\hyperlink{ref-spies2024causalworldmodels}{Spies et al.,
2024}). To facilitate systematic investigation of the effects of
different representations of data on text model performance, we provide
a variety of text output formats. By passing an instance of
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/tokenization.html\#MazeTokenizerModular}{\texttt{MazeTokenizerModular}}
to
\href{https://understanding-search.github.io/maze-dataset/maze_dataset.html\#MazeDataset.as_tokens}{\texttt{as\_tokens(...)}},
a maze can be converted to a text sequence. The
\href{https://understanding-search.github.io/maze-dataset/maze_dataset/tokenization.html\#MazeTokenizerModular}{\texttt{MazeTokenizerModular}}
class contains a rich set of options with class contains 19 discrete
parameters, resulting in over 5.8 million unique possible tokenizers.
All output sequences consist of four token regions representing
different features of the maze; an example output sequence is shown in
\autoref{fig:token-regions}.

>>>>

Autoregressive transformer models can be quite sensitive to the exact
format of input data, and may even use delimiter tokens to perform
reasoning steps (\protect\hyperlink{ref-pfau2024dotbydot}{Pfau et al.,
2024}; \protect\hyperlink{ref-spies2024causalworldmodels}{Spies et al.,
2024}). To facilitate systematic investigation of the effects of
different representations of data on text model performance, we provide
a variety of text output formats, with an example given in
\autoref{fig:token-regions}.
